A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-09-18 doc/large_strain.tex
Update acknowledgments

DD acknowledge the financial support of the German Science Foundation (Deutsche Forschungs-Gemeinschaft, DFG), grant DA 1664/2-1
and the Competence Network for Technical and Scientific High Performance Computing in Bavaria (KONWIHR).
DD, DA and JPP are grateful to Jed Brown (CU Boulder) and Veselin Dobrev (Lawrence Livermore National Laboratory) for a fruitful discussion on matrix-free operator evaluation approaches.
%
{\color{red}
DA was supported ...
%
JPP was supported by ...
}
%
PS acknowledges the support of the Cluster of Excellence Engineering of Advanced Materials (EAM) which made this collaboration possible.

>>>>

D.~Davydov acknowledge the financial support of the German Research Foundation (DFG), grant DA 1664/2-1
and the Competence Network for Technical and Scientific High Performance Computing in Bavaria (KONWIHR).

D.~Davydov, D.~Arndt and J-P.~Pelteret are grateful to Jed Brown (CU Boulder) and Veselin Dobrev (Lawrence Livermore National Laboratory) for a fruitful discussion on matrix-free operator evaluation approaches.

D.~Arndt was supported by the German Research Foundation (DFG) under the project ``High-order discontinuous
Galerkin for the exa-scale'' (\mbox{ExaDG}) within the priority program ``Software
for Exascale Computing'' (SPPEXA).

{\color{red}
J-P.~Pelteret was supported by the European Research Council (ERC) through
the Advanced Grant 289049 MOCOPOLY.(?)
}

P.~Steinmann acknowledges the support of the Cluster of Excellence Engineering of Advanced Materials (EAM) which made this collaboration possible.
